A Triple Origin for Twin Blue Stragglers in Close Binaries

### 2019-02-25 response_to_referees.txt

SPZ/NL:  We have included a sentence here explaining how this relates directly to a prediction for a comparable final orbital period for the proposed outer tertiary.

"Note that part of the mass liberated from the triple system through the second and third Lagrangian points may eventually be accreted back onto the system. This could have interesting consequences for the enrichment of the low-mass white dwarf." - This seems more relevant to point 4? I might even suggest that point 4 be split into two predictions, one having to do with the mass ratio and one having to do with enrichment.

SPZ/NL: Very interesting point. Thanks for pointing this out.
We have edited both of these bullet points as recommended.

Specific notes on the abstract:

Broadly speaking, the abstract is rather unusual in that it is not at all an abstract of the paper but rather a restatement of the predictions in the current Summary. As I wrote above, it is very good that the authors are making explicit predictions. But an abstract is intended to permit a reader to be informed about the entire essential content of a paper, and as such this abstract does not seem appropriately constructed.

SPZ/NL: We think that abstract maybe a bit controversial in comparison
with other abstracts, but we think that it covers the content of the
paper and the presented work.

"are naturally reproduced" - this is an overstatement given the tuning and uncertainties of the simulations; please change to "can be reproduced".

SPZ/NL:  Fixed.
